Illusion Game Validation (Study 1)

### 2022-08-04 study1.Rmd
push new stimuli

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
best_models <- function(data) {
  models <- list()
  for(i in 1:1) {
    for(j in 1:2) {
      for(k1 in c("", "_log")) { 
        for(k2 in c("")) {  
          for(side in c("", "-side")) {
            name <- paste0("dif", k1, i, "-", "str", k2, j, side)
            print(name)
            f <- paste0("poly(Illusion_Difference", 
                        k1,
                        ", ",
                        i,
                        ") * poly(Illusion_Strength",
                        k2, 
                        ", ",
                        j, 
                        ") + (1|Participant)")

@@

model <- brms::brm(formula,
  data = data,
  algorithm = "sampling",
  refresh = 0
)

@@

  n_lines <- 5
  pred <- estimate_relation(model,
                            at = c("Illusion_Strength", "Illusion_Difference"),
                            length = c(25, n_lines)) |>
    mutate(Illusion_Difference = as.factor(round(Illusion_Difference, 2)))

@@

  # Assign color from the same palette to every observation of data (for geom_dots)
  closest <- diffvals[max.col(-abs(outer(data$Illusion_Difference, diffvals, "-")))]
  data$color <- colors[as.character(closest)]
  data$color <- fct_reorder(data$color, closest)

@@

>>>>

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
# plot(seq(0, 1, length.out=100), seq(0, 1, length.out=100)**(1/3), "l", col="green")
# lines(seq(0, 1, length.out=100), sqrt(seq(0, 1, length.out=100)), "l", col="red")
# lines(seq(0, 1, length.out=100), log(1+seq(0, 1, length.out=100)), "l", col="blue")
# lines(seq(0, 1, length.out=100), seq(0, 1, length.out=100), "l", col="black")

best_models <- function(data) {
  models <- list()
  for(i in 1:1) {
    for(j in 1:1) {
      for(k1 in c("", "_log", "_sqrt", "_cbrt")) { 
        for(k2 in c("", "_log", "_sqrt", "_cbrt")) {  
          for(side in c("", "-side")) {
            name <- paste0("dif", k1, i, "-", "str", k2, j, side)
            print(name)
            f <- paste0("poly(Illusion_Difference", 
                        k1,
                        ", ",
                        i,
                        ") * poly(Illusion_Strength",
                        k2, 
                        ", ",
                        j, 
                        ") + (1|Participant)")

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ Illusion_Difference_cbrt * Illusion_Strength + 
    (1 | Participant),
  family = "bernoulli"
)

@@

  vars <- insight::find_predictors(model)$conditional
  n_lines <- length(unique(data[[vars[1]]]))
  pred <- estimate_relation(model,
                            at = vars,
                            length = c(NA, 25))
  pred$Illusion_Difference <- as.factor(round(pred[[vars[1]]], 2))

@@

  # Assign color from the same palette to every observation of data (for geom_dots)
  closest <- diffvals[max.col(-abs(outer(data[[vars[1]]], diffvals, "-")))]
  data$color <- colors[as.character(closest)]
  data$color <- fct_reorder(data$color, closest)

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ Illusion_Difference_cbrt * Illusion_Strength + 
    (1 | Participant),
  family = "bernoulli"
)
